TBA - software evolution, security defects oriented

### 2012-12-20 docs/msr.tex
Change my affiliation

\author{\IEEEauthorblockN{Dimitris Mitropoulos, Vassilios Karakoidas, Georgios Gousios, Panos Louridas
and
Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, gousiosg, louridas, dds\}@aueb.gr}
}
\maketitle

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos \and Vassilios Karakoidas \and Panos Louridas \and Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: \{dimitro, bkarak, gousiosg, louridas, dds\}@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology \\
Email: G.Gousios@tudelft.nl}
}

\maketitle
